Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 trunk/paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes

A full tracing experiment is conducted on \tinto in order to capture an overall power
profile at a much finer resolution. First we run \cosmoart for a full-day simulation
and analyze the power consumption. Second we correlate performance with
power traces of two 1-hor time frames during the day: midday (from 11h-12h) and
midnight (23-24h).

@@

>>>>

A full tracing experiment is conducted on \tinto in order to capture an overall power
profile at a much finer resolution. First we run \cosmoart for a full-day simulation
and analyze the power consumption. Second we correlate performance with
power traces of two 1-hor time frames during the day: mid-day (from 11h-12h) and
midnight (23-24h).

@@

In order to obtain an initial overview of the power dissipation of the system model, Figure~\ref{fig:9} depicts the power profiles of a full-day simulation of \cosmoart leveraging the  polling and blocking MPI policies on the top and bottom plots, respectively. The power profiles shown account for the sum of dissipated power of the 16 nodes used in \tinto captured with our PDUs. The first observation for the polling MPI policy is the quite plain power profile it generated. However the first and last hours of the day along a 24h simulation, dissipate slightly less power than the hours than the mid-day hours. We relate these variations due to the chemical reactions and aerosols, computed by ART, that are taking place during the daylight hours but not during night. In this case peak power dissipation is about 3821\,W.
Looking at the power profile using the blocking MPI policy, we can easily observe
that this pattern is repeated favoring the reduction of power during nighttime hours in a more noticeable way.
